Hybrid platforms and bargaining

### 2024-05-23 src/paper/theory.tex
Add pre-commit hooks

The present paper is closely related to two bodies of literature: a theoretical and an applied one.
Cooperative games with a finite number of atomic players and a continuum of non-atomic ones are called mixed or oceanic games \parencite{milnor1978values}, and have been studied in the cooperative game theory literature.
Most papers in this line of research focus on rather fundamental questions, such as for which games does the Shapley-value exist, when is it unique \parencite{hart1973values}, and whether the various ways of defining it\footnote{
    One can characterize the value of the oceanic game directly, relying on a set of axioms (axiomatic approach). Alternatively the value of an infinite-player game can also be defined as the limit of the value of a series of finite-player games (asymptotic approach).
} lead to the same result \parencite{fogelman1980asymptotic}.\footnote{
    \textcite{hart1973values} shows that in the case of mixed games, the usual axioms do not in general characterize a unique value.
    However, \textcite{fogelman1980asymptotic} demonstrates that, for a quite large subset of games, the asymptotic approach leads to one specific element from the set characterized by the axiomatic approach. 
}
My aim with this paper is both somewhat more general and much more specific in certain aspects.
For one, I focus on the asymptotic approach, and withing that, a specific way of approximating the infinite game of interest.
This is motivated by the fact that I am not interested in the oceanic game per se, but rather in its ability to approximate finite-player games.
Furthermore, I restrict my attention to a specific, but economically important subset of games: those with one indispensable player, and a continuum of fringe players consisting of a finite number of types.
These two restrictions in turn allow me to go beyond the Shapley value, and obtain results for a more general set of solution concepts: random order values.
Additionally, instead of looking at general results, such as existence, I can provide and interpret explicit expressions for the values of the various players.

The other strand of research that is closely related to this paper belongs to the industrial organization literature.
Despite the theoretical appeal and tractability of oceanic games, they, in general, saw remarkably little use in the industrial organization, and, more generally, applied economics.
Nevertheless, there are a few prominent exceptions, such as \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, which use the Shapley value to model wage bargaining under the assumption of divisible labor (continuum of workers).
The first two of these paper also provides microfoundations for using the Shapley value and the weighted value in an intra-firm bargaining setting.
The present paper contributes to this literature by generalizing some of its results, and an examinating some general properties of the various values in the context of such games.
In particular, in addition to the aformentioned papers, the proposed model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using random order values instead of the less general Shapley value or weighted value.
Furthermore, I also provide results for the intersection of two important extensions in \textcite{stole1996intra}: the case of weighted values in the case of multiple types of fringe players.

>>>>

The present paper is closely related to two bodies of literature: a theoretical and an applied one.
Cooperative games with a finite number of atomic players and a continuum of non-atomic ones are called mixed or oceanic games \parencite{milnor1978values}, and have been studied in the cooperative game theory literature.
Most papers in this line of research focus on rather fundamental questions, such as for which games does the Shapley-value exist, when is it unique \parencite{hart1973values}, and whether the various ways of defining it\footnote{
    One can characterize the value of the oceanic game directly, relying on a set of axioms (axiomatic approach). Alternatively the value of an infinite-player game can also be defined as the limit of the value of a series of finite-player games (asymptotic approach).
} lead to the same result \parencite{fogelman1980asymptotic}.\footnote{
    \textcite{hart1973values} shows that in the case of mixed games, the usual axioms do not in general characterize a unique value.
    However, \textcite{fogelman1980asymptotic} demonstrates that, for a quite large subset of games, the asymptotic approach leads to one specific element from the set characterized by the axiomatic approach. 
}
My aim with this paper is both somewhat more general and much more specific in certain aspects.
For one, I focus on the asymptotic approach, and within that, a specific way of approximating the infinite game of interest.
This is motivated by the fact that I am not interested in the oceanic game per se, but rather in its ability to approximate finite-player games.
Furthermore, I restrict my attention to a specific, but economically important subset of games: those with one indispensable player, and a continuum of fringe players consisting of a finite number of types.
These two restrictions in turn allow me to go beyond the Shapley value, and obtain results for a more general set of solution concepts: random order values.
Additionally, instead of looking at general results, such as existence, I can provide and interpret explicit expressions for the values of the various players.

The other strand of research that is closely related to this paper belongs to the industrial organization literature.
Despite the theoretical appeal and tractability of oceanic games, they, in general, saw remarkably little use in the industrial organization, and, more generally, applied economics.
Nevertheless, there are a few prominent exceptions, such as \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, which use the Shapley value to model wage bargaining under the assumption of divisible labor (continuum of workers).
The first two of these paper also provides microfoundations for using the Shapley value and the weighted value in an intra-firm bargaining setting.
The present paper contributes to this literature by generalizing some of its results, and an examination of some general properties of the various values in the context of such games.
In particular, in addition to the aforementioned papers, the proposed model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using random order values instead of the less general Shapley value or weighted value.
Furthermore, I also provide results for the intersection of two important extensions in \textcite{stole1996intra}: the case of weighted values in the case of multiple types of fringe players.

### 2024-05-23 src/presentation/io_day.qmd
Add pre-commit hooks

::: {.fragment}
 - One **platform**: $P$
   - Without the platform, no value can be created
   - Might have its own products (hybrid mdoe)
:::
::: {.fragment}
 - A continuum of potential **fringe entrants**: $F_i, i \in \mathbb{R}_0^+$
   - Infinitesimally small
   - Have one product each
   - Can only sell through the platform
:::

@@

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by seperate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: "best case scenario"
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 p^*_{Ti} = c_T + \mu
 $$
:::

>>>>

::: {.fragment}
 - One **platform**: $P$
   - Without the platform, no value can be created
   - Might have its own products (hybrid mode)
:::
::: {.fragment}
 - A continuum of potential **fringe entrants**: $F_i, i \in \mathbb{R}_0^+$
   - Infinitesimally small
   - Have one product each
   - Can only sell through the platform
:::

@@

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by separate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: "best case scenario"
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 p^*_{Ti} = c_T + \mu
 $$
:::

### 2024-05-23 src/presentation/topics_talk.qmd
Add pre-commit hooks

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by seperate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: "best case scenario"
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 \begin{align*}
 p^*_{Ti} &= c_T + \mu \\
 \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
 \end{align*}
 $$
:::

>>>>

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by separate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: "best case scenario"
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 \begin{align*}
 p^*_{Ti} &= c_T + \mu \\
 \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
 \end{align*}
 $$
:::
